R Python, and Ruby clients for GBIF species occurrence data

### 2017-09-26 manuscript.Rmd
update ms with zenodo DOI, update readme with zenodo badge

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier (DOI). This DOI
corresponds to a snapshot of the GitHub repository at
<https://github.com/sckott/gbifms>. Software can be found at
<https://github.com/ropensci/rgbif>, <https://github.com/sckott/pygbif>,
and <https://github.com/sckott/gibfrb>, all under MIT licenses. We thank
all the users that have used `rgbif`, `pygbif`, and `gbifrb` and have
given feedback and reported bugs. In addition, we greatly appreciate
all the contributors to the three libraries, found at
<https://github.com/ropensci/rgbif/graphs/contributors>,
<https://github.com/sckott/pygbif/graphs/contributors>, and
<https://github.com/sckott/gbifrb/graphs/contributors>.

>>>>

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier
(<https://doi.org/10.5281/zenodo.997547>). This DOI
corresponds to a snapshot of the GitHub repository at
<https://github.com/sckott/gbifms> that matches this preprint. Software
can be found at <https://github.com/ropensci/rgbif>, <https://github.com/sckott/pygbif>,
and <https://github.com/sckott/gibfrb>, all under MIT licenses. We thank
all the users that have used `rgbif`, `pygbif`, and `gbifrb` and have
given feedback and reported bugs. In addition, we greatly appreciate
all the contributors to the three libraries, found at
<https://github.com/ropensci/rgbif/graphs/contributors>,
<https://github.com/sckott/pygbif/graphs/contributors>, and
<https://github.com/sckott/gbifrb/graphs/contributors>.

### 2017-09-26 manuscript.tex
update ms with zenodo DOI, update readme with zenodo badge

Dataset metrics are another useful way of figuring out what datasets you
may want to use. One drawback is that these metrics data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (21687).

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"ropensci/wicket"}\NormalTok{, }\DataTypeTok{force =} \OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

This example comes from \href{https://twitter.com/ajpelu}{Antonio J.
Perez-Luque} who
\href{https://twitter.com/ajpelu/status/473951167567757312}{shared his
plot on Twitter}. Antonio compared the occurrences of Valley Oak
(\emph{Quercus lobata}) from \href{http://www.gbif.org/}{GBIF} to the
distribution of the same species from the
\href{http://esp.cr.usgs.gov/data/little/}{Atlas of US Trees}.

@@

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier (DOI). This DOI
corresponds to a snapshot of the GitHub repository at
\url{https://github.com/sckott/gbifms}. Software can be found at
\url{https://github.com/ropensci/rgbif},
\url{https://github.com/sckott/pygbif}, and
\url{https://github.com/sckott/gibfrb}, all under MIT licenses. We thank
all the users that have used \texttt{rgbif}, \texttt{pygbif}, and
\texttt{gbifrb} and have given feedback and reported bugs. In addition,
we greatly appreciate all the contributors to the three libraries, found
at \url{https://github.com/ropensci/rgbif/graphs/contributors},
\url{https://github.com/sckott/pygbif/graphs/contributors}, and
\url{https://github.com/sckott/gbifrb/graphs/contributors}.

>>>>

Dataset metrics are another useful way of figuring out what datasets you
may want to use. One drawback is that these metrics data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (21697).

@@

@@

This example is inspired by a tweet from
\href{https://twitter.com/ajpelu}{Antonio J. Perez-Luque} who
\href{https://twitter.com/ajpelu/status/473951167567757312}{shared his
plot on Twitter}. Antonio compared the occurrences of Valley Oak
(\emph{Quercus lobata}) from \href{http://www.gbif.org/}{GBIF} to the
distribution of the same species from the
\href{http://esp.cr.usgs.gov/data/little/}{Atlas of US Trees}.

The data in question from the example above is no longer available, so
below we use a different species.

@@

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier
(\url{https://doi.org/10.5281/zenodo.997547}). This DOI corresponds to a
snapshot of the GitHub repository at
\url{https://github.com/sckott/gbifms} that matches this preprint.
Software can be found at \url{https://github.com/ropensci/rgbif},
\url{https://github.com/sckott/pygbif}, and
\url{https://github.com/sckott/gibfrb}, all under MIT licenses. We thank
all the users that have used \texttt{rgbif}, \texttt{pygbif}, and
\texttt{gbifrb} and have given feedback and reported bugs. In addition,
we greatly appreciate all the contributors to the three libraries, found
at \url{https://github.com/ropensci/rgbif/graphs/contributors},
\url{https://github.com/sckott/pygbif/graphs/contributors}, and
\url{https://github.com/sckott/gbifrb/graphs/contributors}.
